---
title: "General Workflow for Rainmaker"
author: "Rebecca Carvin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `Rainmaker` workflow follows this path:

- 1 Aquire precipitation data
- 2 Prepare the data for use in `Rainmaker`
- 3 Determine precipitation event start and end times using `RMevents`
- 4 Compute intensities using `RMintensity`
- 5 Compute erosivity index using `RMerosivity`
- 6 Compute antecedent rainfall using `RMarf`
- 7 Output the results to a file

## 1 Aquire precipitation data
There are many sources for precipitation data. Data for analysis in Rainmaker must have date, time, and rainfall depth values.

One way to access precipitation data is to use the USGS `dataRetrieval` package, which pulls data from NWIS web directly into R. For information on using the USGS dataRetrieval package to import data from NWIS web into R refer to:

INSERT LINK TO DATARETRIEVAL DOCUMENTATION HERE

A quick workflow for USGS `dataRetrieval` to pull precipitation data:
 
```{r}
library("dataRetrieval")
siteNumber <- "441624088045601"
parameterCd <- "00045"    # Precipitation
precip_raw <- readNWISuv(siteNumber, parameterCd, "2014-10-01", "2014-11-30" ,
                         tz = "America/Chicago")
precip_raw <- renameNWISColumns(precip_raw)
```

If not using `dataRetrieval` then read the data into R using read.csv. If you have multiple input files to run through rainmaker, t is a good idea to set a working directory that points R to their location.

For example:
```{r}
#setwd("H:/R/precipitation-data")
#precip_raw <- read.csv("example.csv")
```

## 2 Prepare the data for use in `Rainmaker`
The user must get the data into a format acceptable for use in Rainmaker. Date and time must be in POSIXct format. The user may choose to convert their dates and times into POSIXct on their own, or may use the RMprep function. 
###RMprep

---
Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
